---
title: "Worksheet 3b"
author: "Joseph Bennett P. Dairo"
date: "23/11/2022"
output: pdf_document
---

#Josep Bennett P. Dairo

#1
##a.
```{r}
data_Frame <- data.frame(Respondents= (1:20), 
                Sex= c(2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2), 
                Fathers_occupation= c(1, 3, 3, 3, 1, 2, 3, 1, 1, 1, 3, 2, 1, 3, 3, 1, 3, 1, 2, 1),
                Persons_at_home= c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 5, 4, 7, 8, 8, 3, 11, 7, 6), 
                Siblings_at_school= c(6, 4, 4, 1, 2, 1, 5, 3, 1 ,2, 3, 2, 5, 5, 2, 1, 2, 5, 3, 2),
                Types_of_houses= c(1, 2, 3, 1, 1, 3, 3, 1, 2, 3, 2, 3, 2, 2, 3, 3, 3, 3, 3, 2))
data_Frame
```
##b.
```{r}
summary(data_Frame)
```
## summary displayed the Min, 1st Qu., Median, Mean, 3rd Qu., and Max 
## The data has male and female respondents, fathers occupation, persons at home, and siblings at school. This is a survey ##data. 
   
##c. 
##Answer: No, siblings at school has 2.95 mean

##d.
```{r}
subset(data_Frame[1:2, ])
```
##e.
```{r}
subset(data_Frame[3:5, 2:4])
```
##f.
```{r}
library(dplyr)
house_Types <- select(data_Frame, Types_of_houses)
house_Types
```
##g.
```{r}
respondents_Father <- subset(data_Frame[c(1:20),c(1:3)])
respondents_Father
male <- respondents_Father[data_Frame$Sex == '1',]
male
```
## output: There is no male respondent with a father that is a farmer

##h.
```{r}
data1 <- subset(data_Frame[c(1:20),c(1,2,5)])
data1
female <- data1[data_Frame$Sex == '2',]
female
call <- data_Frame[,5] >= 5
call
sum(call)
data1[call,]
```
## output: There are 5 female respondents
## that have greater than or equal to 5 number of siblings attending school


#2)
```{r}
df = data.frame(Ints=integer(),Doubles=double(), Characters=character(), Logicals=logical(),
                Factors=factor(), stringsAsFactors=FALSE)
print("Structure of the empty dataframe:")
print(str(df))
```
#a.
# results it displayed whats inside the data frame which are empty, 0 obs. of 5 variables.
# Instead of displaying <0 rows> (or 0-length row.names) it displayed:
# 'data.frame':	0 obs. of  5 variables:
# $ Ints      : int 
# $ Doubles   : num 
# $ Characters: chr 
# $ Logicals  : logi 
# $ Factors   : Factor w/ 0 levels: 
#  NULL
# Due to print(str(df)) it displayed the varibles of the dataset in vertical with the 
# following functions. 

#3)

# The title of the bar graph is sentiments of tweets per day. It has a legend at the right
# side, red for negative, yellow for neutral, and blue for positive. In day 1
# July 14, 2020 the negative sentiments almost reach 2,500. In day 2 July 15, 2020 the 
# negative sentiments sky rocketed to 4,000 plus. While in day 3 and 4 negative sentiments 
# went down around 3,000 plus. Then day 5 it went down again to 2,000 plus then went up at 
# day 6. The graph is mostly negative sentiments from day 1 to 6.
